R Notebook

### 2017-03-30 doc/RMD/data-comparison.Rmd
rerun with dplyr specified

```{r, equal_sets}
setequal(saj, syd)
```

@@

```{r}
syddiff <- setdiff(syd, saj)
sajdiff <- setdiff(saj, syd)
the_difference <- bind_rows(syd = syddiff, saj = sajdiff, .id = "source") %>% arrange(Isolate)
head(the_difference, n = 20)
```

>>>>

```{r, equal_sets}
dplyr::setequal(saj, syd)
```

@@

```{r}
syddiff <- dplyr::setdiff(syd, saj)
sajdiff <- dplyr::setdiff(saj, syd)
the_difference <- bind_rows(syd = syddiff, saj = sajdiff, .id = "source") %>% arrange(Isolate)
head(the_difference, n = 20)
```
